### 2015-05-14 whoop.tex
fixes

\noindent\textbf{Identifying Locks }
%
When the instrumentation phase begins, \whoop performs an inter-procedural static analysis (on the Boogie IVL source code of each entry point) to identify all available locks and rewrite each one (both at declaration and at all access sites) to a unique constant Boogie variable. The reason behind this transformation, is that representing all locks statically, instead of their original SMACK pointer-based representation, helps \whoop perform various internal instrumentation and optimization passes.
%
Currently, \whoop only supports mutexes and spinlocks that are available in the Linux kernel APIs. However, it is relatively easy to enhance our tool with knowledge of other locking primitives. If \whoop cannot infer a lock, e.g. because it was created dynamically or was indexed from an array of locks, it will exit with a warning. The are two reasons behind this: (i) it is arguably hard to detect such locks using static analysis; and (ii) a small, fixed number of locks is advocated by Linux experts as good practice when developing drivers~\cite{corbet2005linux}.

@@

\noindent\textbf{Verification and Error Reporting }
%
For each pair of entry points, the instrumented sequential program, equipped with procedure and loop summaries, is sent to the Boogie verification engine. Boogie generates a VC, for each procedure in the program, and discharges it to the Z3~\cite{de2008z3} theorem prover.  In particular, the verification for the root-level procedure, encoding the sequential program sketched in Figure~\ref{fig:sequentialization}, encodes the race-freedom check for the entry point pair. Successful verification implies that the entry point pair is free of data races, while an error (i.e.\ counterexample) denotes a \emph{potential} data race and is reported to the user. To improve usability, \whoop has a built-in error reporter that matches counterexamples to source code. The following is a race that \whoop found and reported for the example of Figure~\ref{fig:data_race_example}:

>>>>

\noindent\textbf{Identifying Locks }
%
When the instrumentation phase begins, \whoop performs an inter-procedural static analysis (on the Boogie IVL source code of each entry point) to identify all available locks and rewrite each one (both at declaration and at all access sites) to a unique constant Boogie variable. The reason behind this transformation is that representing all locks statically, instead of their original SMACK pointer-based representation, helps \whoop perform various internal instrumentation and optimization passes.
%
Currently, \whoop only supports mutexes and spinlocks that are available in the Linux kernel APIs. However, it is relatively easy to enhance our tool with knowledge of other locking primitives. If \whoop cannot infer a lock, e.g. because it was created dynamically or was indexed from an array of locks, it will exit with a warning. The are two reasons behind this: (i) it is arguably hard to detect such locks using static analysis; and (ii) a small, fixed number of locks is advocated by Linux experts as good practice when developing drivers~\cite{corbet2005linux}.

@@

\noindent\textbf{Verification and Error Reporting }
%
For each pair of entry points, the instrumented sequential program, equipped with procedure and loop summaries, is sent to the Boogie verification engine. Boogie generates a VC, for each procedure in the program, and discharges it to the Z3 theorem prover.  In particular, the verification for the root-level procedure, encoding the sequential program sketched in Figure~\ref{fig:sequentialization}, encodes the race-freedom check for the entry point pair. Successful verification implies that the entry point pair is free of data races, while an error (i.e.\ counterexample) denotes a \emph{potential} data race and is reported to the user. To improve usability, \whoop has a built-in error reporter that matches counterexamples to source code. The following is a race that \whoop found and reported for the example of Figure~\ref{fig:data_race_example}:
